Timeliness of security updates for Android

### 2015-03-20 securityupdates.tex
Rename Experiment to Analysis

\section{Experiments}
\label{sec:results}
We present the results of our analysis showing that, on average, \daMeanInsecurityPerc\ of Android devices are exposed to critical vulnerabilities.
Devices, on average, apply \daUpdatesPerYear\ updates each year and \daPercUpdatesDowngrades\ of full version changes are downgrades to older versions.
We describe three experiments, examining the vulnerability of Android devices in general (\S\ref{sec:exp:versionsecurity}), explore the upgrade cycle and vulnerability cycle of the ecosystem (\S\ref{sec:exp:android_ecosystem}) and quantify the updates installed on particular devices (\S\ref{sec:exp:device_updates}).

\subsection{Experiment 1: vulnerability of Android devices}\label{sec:exp:versionsecurity}

@@

\subsection{Experiment 2: behaviour of the Android ecosystem}\label{sec:exp:android_ecosystem}

\subsubsection{Method} As in Experiment 1, we used the version information for each device to calculate which critical vulnerabilities each device was susceptible to on a daily basis.

@@

\subsection{Experiment 3: Updates to particular devices}\label{sec:exp:device_updates}
Previous graphs summarise data across all the devices, however one of the advantages of the \da\ data is that we can look at what happens to individual devices over time.
This allows us to determine whether newer OS versions are being used because people are buying new phones running newer OS versions or whether existing devices receive updates.

@@

\subsubsection{Method}
As in Experiment 1, we used the version information for each device to calculate which critical vulnerabilities each device was susceptible to on a daily basis.
We also recorded when the version changed and which versions it changed from and to.
In the \da\ data we have over 1000 devices contributing data in any particular week.
However most devices only contribute for a short period of time and so we do not observe updates happening on every device.
Instead we have a hopefully representative sample of updates which happened while \da\ was installed on the devices.
\da\ cannot distinguish between a device being replaced and the \da\ app being removed as while multiple devices can be linked to the same user account, that is a manual process and few users do it.

>>>>

\section{Analysis}
\label{sec:results}
We present the results of our analysis showing that, on average, \daMeanInsecurityPerc\ of Android devices are exposed to critical vulnerabilities.
Devices, on average, apply \daUpdatesPerYear\ updates each year and \daPercUpdatesDowngrades\ of full version changes are downgrades to older versions.
We describe three analyses, examining the vulnerability of Android devices in general (\S\ref{sec:exp:versionsecurity}), explore the upgrade cycle and vulnerability cycle of the ecosystem (\S\ref{sec:exp:android_ecosystem}) and quantify the updates installed on particular devices (\S\ref{sec:exp:device_updates}).

\subsection{Analysis 1: vulnerability of Android devices}\label{sec:exp:versionsecurity}

@@

\subsection{Analysis 2: behaviour of the Android ecosystem}\label{sec:exp:android_ecosystem}

\subsubsection{Method} As in Analysis 1, we used the version information for each device to calculate which critical vulnerabilities each device was susceptible to on a daily basis.

@@

\subsection{Analysis 3: Updates to particular devices}\label{sec:exp:device_updates}
Previous graphs summarise data across all the devices, however one of the advantages of the \da\ data is that we can look at what happens to individual devices over time.
This allows us to determine whether newer OS versions are being used because people are buying new phones running newer OS versions or whether existing devices receive updates.

@@

\subsubsection{Method}
As in Analysis 1, we used the version information for each device to calculate which critical vulnerabilities each device was susceptible to on a daily basis.
We also recorded when the version changed and which versions it changed from and to.
In the \da\ data we have over 1000 devices contributing data in any particular week.
However most devices only contribute for a short period of time and so we do not observe updates happening on every device.
Instead we have a hopefully representative sample of updates which happened while \da\ was installed on the devices.
\da\ cannot distinguish between a device being replaced and the \da\ app being removed as while multiple devices can be linked to the same user account, that is a manual process and few users do it.
